Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2018-11-08 man/figures/growth_changes.Rmd
ya casi lo tengo

plotGC <- function(df, y, yse, x, my_ylab, micolor, xrange, ...){ 
  # Get error bar aesthetic
  yerrorbar <- aes_string(ymin = paste(y, yse, sep = '-'),
                         ymax = paste(y, yse, sep = '+'))

  p <- ggplot(df, aes_string(x = x, y = y)) +
    geom_errorbar(mapping = yerrorbar, colour='gray', width=.35, size=.3) + 
    geom_bar(stat='identity', fill=micolor, colour=micolor) +
    geom_hline(yintercept = 0, colour = 'black', lwd = 0.3) + 
    ylab(my_ylab) +
    # Add line to %GC = 50 
    geom_hline(yintercept=c(50, -50), linetype=2, colour='black') +
    theme_bw() +
    theme(panel.grid = element_blank()) +
    # Customize limits and breaks to min of year data 
    scale_x_continuous(limits = c(min(xrange), max(xrange)), 
                       breaks = xrange, 
                       sec.axis = dup_axis())
  p
}

@@

gc_todos %>% dplyr::filter(site == 'gc_caH') %>% 
  plotGC(y = 'gc_md', yse = 'gc_md_se', x = 'year', 
       my_ylab = '% GC', micolor = "#838B8B", xrange=xrange)

@@

gc_todos %>% dplyr::filter(site != 'gc_sj') %>% 
  plotGC(y = 'gc_md', yse = 'gc_md_se', x = 'year', 
       my_ylab = NULL, micolor = "#838B8B", xrange=xrange) + 
  facet_rep_wrap(~site, ncol = 1) + 
  theme(panel.spacing = unit(5, "lines"),
        strip.placement = "inside", 
        strip.background = element_blank())

>>>>

plotGC <- function(df, y, yse, x, my_ylab, 
                   micolor, ...){ 
  # Get error bar aesthetic
  yerrorbar <- aes_string(ymin = paste(y, yse, sep = '-'),
                         ymax = paste(y, yse, sep = '+'))

  p <- ggplot(df, aes_string(x = x, y = y)) +
    geom_errorbar(mapping = yerrorbar, colour = 'gray', width = .35, size = .3) + 
    geom_bar(stat = 'identity', fill = micolor, colour = micolor) +
    geom_hline(yintercept = 0, colour = 'black', lwd = 0.3) + 
    ylab(my_ylab) +
    # Add line to %GC = 50 
    geom_hline(yintercept = c(50, -50), linetype=2, colour='black') +
    theme_bw() +
    theme(panel.grid = element_blank()) 
    # Customize limits and breaks to min of year data 
  p
}

@@

    scale_x_continuous(limits = limitesx, 
                       breaks = xrange, 
                       position = pos) 
                       #sec.axis = dup_axis(name = NULL))

# Get automatically limits of y for caH anc caL
minimoY <- min((gc_todos %>% 
      dplyr::filter(site != 'gc_sj' & gc_md < 0) %>% 
      mutate(error = gc_md - gc_md_se))$error, na.rm = TRUE)

maximoY <- max((gc_todos %>% 
      dplyr::filter(site != 'gc_sj' & gc_md > 0) %>% 
      mutate(error = gc_md + gc_md_se))$error, na.rm = TRUE)

# Ojo ver limites de ylim 
# ggplot_build(pcaL)$layout$panel_params[[1]]$y.range
# ggplot_build(pcaH)$layout$panel_params[[1]]$y.range

# Establece rango de datos para y 
mismo_y <- scale_y_continuous(limits=c(minimoY, maximoY), 
                             breaks = c(-100, -50, 0, 50, 50, 100, 150))

mismo_x <- scale_x_continuous(limits=c(min(gc_todos$year), max(gc_todos$year)), 
                             breaks = xrange, position = 'bottom')

#### --> Hay un error con la localizacion de las barras de error en el eje x. REVISAR

pcaH <- gc_todos %>% dplyr::filter(site == 'gc_caH') %>% 
  plotGC(y = 'gc_md', yse = 'gc_md_se', x = 'year', 
         my_ylab = '% GC', micolor = "#838B8B") + mismo_y + mismo_x +
  annotate("text", x = 1990, y = 120, label = "CA-High", fontface = 2, size = 5)

pcaL <- gc_todos %>% dplyr::filter(site == 'gc_caL') %>% 
  plotGC(y = 'gc_md', yse = 'gc_md_se', x = 'year',
         my_ylab = '% GC', micolor = "#838B8B") +  
         # xrange=xrange, pos = 'bottom', limitesx = limitesx) + 
  ylab('') + mismo_y + mismo_x + 
  annotate("text", x = 1990, y = 120, label = "CA-Low", fontface = 2, size = 5)

psj <- gc_todos %>% dplyr::filter(site == 'gc_sj') %>% 
  plotGC(y = 'gc_md', yse = 'gc_md_se', x = 'year', 
         my_ylab = '% GC', micolor = "#838B8B") + 
         # xrange=xrange, pos = 'top', limitesx = limitesx) + 
  ylab('') + xlab('') + 
  scale_y_continuous(trans = pos_neg_log, 
                     breaks=c(-1000, -500, -100, 0, 100, 500)) + mismo_x + 
  geom_hline(yintercept = 1) +
  annotate("text", x = 1990, y = 500, label = "SJ", fontface = 2, size = 5)

c(-116, 150)

ggplot_build(pcaH)$layout$panel_scales_y[[1]]$range$range
ggplot_build(gccaL)$layout$panel_scales_y[[1]]$range$range

layer_scales(pcaH)$y$range$range

layer_scales(c)$x$range$range[2]) +

@@

gc_todos %>% dplyr::filter(site != 'gc_sj') %>% 
  plotGC(y = 'gc_md', yse = 'gc_md_se', x = 'year', 
       my_ylab = NULL, micolor = "#838B8B", xrange=xrange) + 
  facet_rep_wrap(~site, ncol = 1, strip.position = 'bottom') + 
  theme(panel.spacing = unit(0, "lines"),
        strip.placement = "outside", 
        strip.background = element_blank())
